Precise Weed and Maize classification through Convolutional Neuronal Networks

### 2017-07-22 PaperBCJ.tex
cambios21dejulio
cambios despues de revision

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{C\'ordova-Cruzatty Andrea \IEEEauthorrefmark{1},
Barreno Barreno Mauricio Daniel \IEEEauthorrefmark{2} and J\'acome Barrionuevo Jos\'e Misael \IEEEauthorrefmark{3}}
\IEEEauthorblockA{Department of Energy and Mechanics,
University of the Army ESPE\\
Latacunga - Quijano y Ordo\~nez and Hermanas Pa\'ez \\
Email: \IEEEauthorrefmark{1}accordova@espe.edu.ec,
\IEEEauthorrefmark{2}mdbarreno@espe.edu.ec,
\IEEEauthorrefmark{3}jmjacome1@espe.edu.ec}}
% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

@@

Deep Learning has played an important role in modern times, being widely used in artificial vision applications and specifically in pattern recognition. The versatility of deep learning has positioned it as a fit tool used in many fields of application, among which is precision agriculture. This paper presents the development of an algorithm that has two stages; one for image segmentation and another for classification. Segmentation is intended to separate the target plant from the original image, while classification is meant to identify what images belong to the two classes defined. The study uses a convolutional neural network (CNN) with two classes applied for the classification between maize plants and weeds in real time, focused on maize crops in their initial development stages. This network has been trained with a dataset generated through the segmentation stage. The performance of the network was analyzed and compared with different network architectures. The network architecture that presented the best training results was chosen and afterwards its number of filters were reduced in order to analyze its behavior. Finally, the resulting network was tested on different processors to compare classification speed of each and determine which one could be used for an autonomous system in a real-time application.\\

@@

\section{Introduction}
During the last centuries, significant progress has taken place in science and technology developments. Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial sectors, providing new means to approach problems in a different manner. 
\\

The availability of leading edge technologies has considerably increased, thus becoming more accessible to people. This effect of globalization has allowed many countries to have access to state-of-the-art technological products, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems. 
\\

Technological advances have caused industry transformations; manufacturing, food processing, and information industries among others, have gone through dramatic changes with the new industrial revolution. However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry. Agriculture in Ecuador has undergone some changes since colonial times; while it is true that there are efficient agricultural practices, the lack of technological resources make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer. Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality, which leads the new research efforts towards finding alternative solutions to weed control issues. 
\\

@@

One of the first approximations for crop detection algorithms was developed in 1996 \cite{brivot1996segmentation}; this algorithm could segment crops from weeds by means of infrared (IR) Images. The images were processed by a hysteresis umbral and the Min Neighbouring method to identify the rows of a crop. In recent years the implementation of machine learning has opened new possibilities in weed and crop differentiation process. Recently, the use of Harris Corner detection techniques in CNNs was implemented with the use of Feature Detection, a machine-learning algorithm that uses DBSCAN (Density-based spartial clustering of aplications with noise) \cite{cheng2015feature}. This algorithm demonstrated an effectiveness of 98\% in the identification of rice weeds. Araguez \textit{et. al} \cite{equipo2006proceedings} implemented a segmentation algorithm through the analysis of the green histogram of the image and performed the crop and weed segmentation with unspecified classifiers in their document.
\\

@@

For the training and image-capturing stages, the following elements were used: a Raspberry Pi 3 with a V2.1 Pi camera for image acquisition. The system was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images. Due to the popularity of GPU computing for its advantages in the development of models of Convolutional Neural Networks, such as a better processing speed, it was necessary to consider hardware compatible with parallel computing devices such as the Graphic Cards manufactured by NVIDIA. These cards have the advantage of a superior processing speed compared to a CPU in order to optimize image-processing time and deep learning Model's training process, thus the selected device was a computer with a Nvidia graphics card GTX950M. Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, with an ARM Cortex-A53, 1.2GHz, and 4 cores, in order to test their performance for a future application in an independent mobile system that could be implemented in an embedded system. The hardware chosen will be tested to classify images, in each classification a measurement of the processing time will be taken to later on analyze if the hardware can process information in real time. 
\\

@@

Due to the lack of local weed and maize plants datasets, it was necessary to search for maize crops. The initial development stage of maize was selected because actions taken by the farmer during this stage are easier to execute and these will impact the future crop yield. Fieldwork at a nearby town called P\'illaro was arranged with the purpose of obtaining image samples. P\'illaro is a city located in the Tungurahua Province, in the center of the Ecuadorian Highlands region, it is a recognized andean-crop producer of species such as: maize, potatoes and a wide variety of fruits. Due to its year-long production season, many maize crops at its initial development stage were found in this area. \\

@@

Also, it was necessary to obtain images of the most common weed plants found in maize crops in Pillaro, in order to allow the network to discriminate between the two defined classes in the dataset: maize and weeds. \\
\begin{comment}
Entonces, a traves de un proceso de procesamiento digital de imagenes, como primera fase, la imagen fue normalizada en su canal verde, esto mejora la deteccion del color verde porque elimina las luces y las sombras de la imagen, despues extrajimos el color verde de la imagen con la ecuacion descrita opr Wang, Men, Luo and Mei, para obtener una imagen final en escala de grises, despues se aplico una Umbralizacion de OTSU para obtener una mascara binaria 
\end{comment}

@@

One of the characteristics of CNN is that these can have multiple architectures, each architecture can reach different results depending on the application. For the present document four CNN architectures have been considered. Two arquitectures were chosen from the Caffe Zoo Model(a free resource provided by Caffe Developers): LeNet and AlexNet. Also, Potena and Nardi\cite{potena2016fast} used two additional types of architectures, sNET and cNET, which sucessfully proved an aceptable performance in plants and crop identification processes. With the four Nets chosen, each one was trained with the same solver of type Adam and with the same dataset. The training results are shown on table \ref{table:2}. \\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
 Accuracy(\%) & 86.48 & 93.86 & 96.4 & 80.4 \\
 Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\caption{Comparison of the 4 types of CNN}
\label{table:2}
\end{table}

@@

Although results given by this type of network are excellent, one of the main purposes of this paper was the implementation of this system in real time. The number of parameters to be computed by the selected network were numerous, so it is necessary to make network modifications in order to improve its processing speed. To achieve this, it was necessary to reduce the number of filters of cNET from 64 to 16. This final number of filters used in the network was selected because this is the minimum number of filters that allow to maintain training accuracy. \\

@@

Thus, the complete network model was conformed by the following components: an input layer where an RGB image of 64x64 pixels is received, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel (this layer only obtains the main characteristics of the image), then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a value of kernel size and stride of 2. Then again a second layer of convolution that has 16 filters is applied, the size of kernel is 5 and the stride is 1, followed by a new layer of pooling with a kernel size and stride of 2, so the resulting image had a size of 16x16x16. Finally, the network is completed with three consecutive fully-connected layers; the first with 384 neurons, the next with 192 and the last with 2 neurons. The type of layers fully-connected contain a total of 478 neurons, where the last two neurons that are the output represent the two classes to identify. The resulting model is shown in figure \ref{figure4}. \\

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{C\'ordova-Cruzatty Andrea \IEEEauthorrefmark{1},
Barreno Barreno Mauricio Daniel \IEEEauthorrefmark{2} and J\'acome Barrionuevo Jos\'e Misael \IEEEauthorrefmark{3}}
\IEEEauthorblockA{Department of Energy and Mechanics,
University of the Armed Forces ESPE\\
Latacunga - Quijano y Ordo\~nez and Hermanas Pa\'ez \\
Email: \IEEEauthorrefmark{1}accordova@espe.edu.ec,
\IEEEauthorrefmark{2}mdbarreno@espe.edu.ec,
\IEEEauthorrefmark{3}jmjacome1@espe.edu.ec}}
% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

@@

Deep Learning is playing an important role in big data processing for more accurate modeling of common productive processes. It is being widely used in artificial vision applications and specifically in pattern recognition. The versatility of deep learning has positioned it as a fit tool used in many fields of application, among which is precision agriculture. This paper presents the development of an algorithm capable of image segmentation and classification. Segmentation is intended to separate the target plant from the original image, while classification is meant to identify what images belong to the two defined classes. It applies a convolutional neural network (CNN) to discriminate maize plants from weeds in real time, at early crop development stages. It was applied to maize crop because it is a common staple crop in the Ecuadorian Highlands.  The convolutional neural network has been trained with a dataset generated in the segmentation stage. The performance of the network was analyzed with LeNET, AlexNet, cNET and sNET network architectures. The network architecture that presented the best training results was cNET based on its performance in terms of accuracy (96.4\%) and processing time of 161 miliseconds in a Raspberry Pi CPU. The minimum working filter number for this network architecture was 16.The best performing algorithms and processors have a significant potential for autonomous weed and crop classification systems in a real-time application.\\

@@

\section{Introduction}
During the last centuries, significant progress has taken place in science and technology developments. Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial and productive sectors, providing new means to approach problems in a different manner. The availability of leading edge technologies has considerably increased, thus becoming more accessible to people. This effect of globalization has allowed many countries to have access to state-of-the-art technological products, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems. 
\\

Technological advances have caused industry transformations; manufacturing, food processing, and information industries among others, have gone through dramatic changes with the new industrial revolution. However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry. Agriculture in Ecuador has undergone some changes since colonial times; while it is true that there are efficient agricultural practices, the lack of technological resources and applications make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer. Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality, which leads the new research efforts towards finding alternative solutions to weed control aspects. 
\\

@@

One of the first approximations for crop detection algorithms was developed in 1996 \cite{brivot1996segmentation}; this algorithm could segment crops from weeds by means of infrared (IR) Images. The images were processed by a hysteresis umbral and the Min Neighbouring method to identify the rows of a crop. In recent years the implementation of machine learning has opened new possibilities in weed and crop differentiation process. Recently, the use of Harris Corner detection techniques in CNNs was implemented with the use of Feature Detection, a machine-learning algorithm that uses DBSCAN (Density-based spartial clustering of aplications with noise) \cite{cheng2015feature}. This algorithm demonstrated an effectiveness of 98\% in the identification of rice weeds. Araguez \textit{et. al} \cite{equipo2006proceedings} implemented a segmentation algorithm through the analysis of the green histogram of the image and performed the crop and weed segmentation with unspecified classifiers.
\\

@@

A Raspberry Pi 3 with a V2.1 Pi camera for image acquisition was used for the training and image-capturing stages. The system was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images. Due to the popularity of GPU computing for its advantages in the development of models of Convolutional Neural Networks, such as a better processing speed, it was necessary to consider hardware compatible with parallel computing devices such as the Graphic Cards manufactured by NVIDIA. These cards have the advantage of a superior processing speed compared to a CPU in order to optimize image-processing time and deep learning Model's training process, thus the selected device was a computer with a Nvidia graphics card GTX950M. Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, with an ARM Cortex-A53, 1.2GHz, and 4 cores, in order to test their performance for a future application in an independent mobile system that could be implemented in an embedded system. The hardware chosen will be tested to classify images, in each classification a measurement of the processing time will be taken to later on analyze if the hardware can process information in real time. 
\\

@@

Due to the lack of local weed and maize plants datasets, it was necessary to search for maize crops. The initial development stage of maize was selected because actions taken by the farmer during this stage are easier to execute and these will impact the future crop yield. Fieldwork at a nearby town called P\'illaro was arranged with the purpose of obtaining image samples. P\'illaro is a city located in the Tungurahua Province, in the center of the Ecuadorian Highlands region, it is a recognized andean-crop producer of species such as maize, potatoes and a wide variety of fruits. Due to its year-long production season, many maize crops at its initial development stage were found in this area. \\

@@

Also, it was necessary to obtain images of the most common weed plants found in maize crops in P\'illaro, in order to allow the network to discriminate between maize and weeds. \\
\begin{comment}
Entonces, a traves de un proceso de procesamiento digital de imagenes, como primera fase, la imagen fue normalizada en su canal verde, esto mejora la deteccion del color verde porque elimina las luces y las sombras de la imagen, despues extrajimos el color verde de la imagen con la ecuacion descrita opr Wang, Men, Luo and Mei, para obtener una imagen final en escala de grises, despues se aplico una Umbralizacion de OTSU para obtener una mascara binaria 
\end{comment}

@@

One of the characteristics of CNN is that these can have multiple architectures, each architecture can reach different results depending on the application. For the present document four CNN architectures have been considered. Two arquitectures were chosen from the Caffe Zoo Model(a free resource provided by Caffe Developers), LeNet and AlexNet. Also, Potena and Nardi\cite{potena2016fast} used two additional types of architectures, sNET and cNET, which sucessfully proved an aceptable performance in plants and crop identification processes. With the four Nets chosen, each one was trained with the same solver of type Adam and with the same dataset. The training results are shown on table \ref{table:2}. \\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
 Accuracy(\%) & 86.48 & 93.86 & 96.4 & 80.4 \\
 Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\caption{Comparison of the 4 types of CNN}
\label{table:2}
\end{table}

@@

Although results given by this type of network are excellent, one of the main purposes of this paper was the implementation of this system in real time. The number of parameters to be computed by the selected network were numerous, so it was necessary to make network modifications in order to improve its processing speed. To achieve this, it was necessary to reduce the number of filters of cNET from 64 to 16. This final number of filters used in the network was selected because this is the minimum number of filters that maintain an acceptable training accuracy. \\

@@

Thus, the complete network model was conformed by an input layer where an RGB image of 64x64 pixels is received, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel (this layer only obtains the main characteristics of the image), then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a value of kernel size and stride of 2. Then again a second layer of convolution that has 16 filters is applied, the size of kernel is 5 and the stride is 1, followed by a new layer of pooling with a kernel size and stride of 2, so the resulting image had a size of 16x16x16. Finally, the network is completed with three consecutive fully-connected layers; the first with 384 neurons, the next with 192 and the last with 2 neurons. The type of layers fully-connected contain a total of 478 neurons, where the last two neurons that are the output represent the two classes to identify. The resulting model is shown in figure \ref{figure4}. \\
